FictionEro - Data Cleaning

### 2024-01-26 analysis/1_cleaning.qmd
stabilize re-ordering of participants and update data

```{r}
df <- read.csv("../data/rawdata_participants.csv")
dftask <- read.csv("../data/rawdata_task.csv")
```

@@

```{r}
data.frame(Comments = trimws(df$Feedback_Comments[df$Feedback_Comments != ""])) |> 
  filter(!Comments %in% c("No", "Nope", "nope", "None")) |> 
  knitr::kable()
```

@@

dftask |> 
  group_by(Participant, Type) |> 
  summarise(Arousal = mean(Arousal), 
            Valence = mean(Valence),
            Enticement = mean(Enticement),
            .groups = "drop") |>
  pivot_wider(names_from = Type, values_from = all_of(c("Arousal", "Valence", "Enticement"))) |>
  transmute(Participant = Participant,
            d_Arousal = Arousal_Erotic - `Arousal_Non-erotic`,
            d_Valence = Valence_Erotic - `Valence_Non-erotic`,
            d_Enticement = Enticement_Erotic - `Enticement_Non-erotic`) |>
  mutate(Participant = fct_reorder(Participant, d_Arousal)) |> 
  pivot_longer(-Participant) |> 
  mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
  ggplot(aes(x=value, y=Participant, fill=Group)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  theme_bw() +
  labs(title = "Difference between Erotic and Neutral", x="Erotic - Neutral") +
  facet_wrap(~name, ncol=3, scales="free_x")
```

@@

```{r p_demographics_sexorient}
p_sexorient <- df |>
  ggplot(aes(x = SexualOrientation)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x = "Sexual Orientation", y = "Number of Participants", title = "Sexual Orientation") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_sexorient
```

```{r p_demographics_sexactivity}
p_sexactivity <- df |>
  ggplot(aes(x = SexualActivity)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x = "Last Sexual Activity", y = "Number of Participants", title = "Time of Last Sexual Activity") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
p_sexactivity
```

>>>>

df <- read.csv("../data/rawdata_participants.csv")
dftask <- read.csv("../data/rawdata_task.csv")
```

@@

```{r}
data.frame(Comments = trimws(df$Feedback_Comments[df$Feedback_Comments != ""])) |> 
  filter(!Comments %in% c("No", "Nope", "nope", "None", "ba")) |> 
  knitr::kable()
```

@@

dftask |> 
  filter(Relevance %in% c("Relevant", "Non-erotic")) |> 
  group_by(Participant, Type) |> 
  summarise(Arousal = mean(Arousal), 
            Valence = mean(Valence),
            Enticement = mean(Enticement),
            .groups = "drop") |>
  pivot_wider(names_from = Type, values_from = all_of(c("Arousal", "Valence", "Enticement"))) |>
  transmute(Participant = Participant,
            d_Arousal = Arousal_Erotic - `Arousal_Non-erotic`,
            d_Valence = Valence_Erotic - `Valence_Non-erotic`,
            d_Enticement = Enticement_Erotic - `Enticement_Non-erotic`) |>
  filter(!is.na(d_Arousal)) |> 
  mutate(Participant = fct_reorder(Participant, d_Arousal)) |> 
  pivot_longer(-Participant) |> 
  mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
  ggplot(aes(x=value, y=Participant, fill=Group)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  theme_bw() +
  labs(title = "Difference between Erotic and Neutral", x="Erotic - Neutral") +
  facet_wrap(~name, ncol=3, scales="free_x")
```

@@

```{r p_demographics_sexorient}
p_sexorient <- df |>
  ggplot(aes(x = SexualOrientation, fill=Sex)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292")) +
  labs(x = "Sexual Orientation", y = "Number of Participants", title = "Sexual Orientation") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_sexorient
```

```{r p_demographics_sexactivity}
p_sexactivity <- df |>
  ggplot(aes(x = SexualActivity, fill=Sex)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292")) +
  labs(x = "Last Sexual Activity", y = "Number of Participants", title = "Time of Last Sexual Activity") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
p_sexactivity
```
